Type Error Telemetry at Scale

### 2023-09-28 programming23/paper.tex
transpose size / dist tables to save space

\usepackage{alltt}
% Not sure why <Programming> is recommending non-standard tools
% \usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
% Errors with
% ! Undefined control sequence.
% <argument> \l__siunitx_number_implicit_plus_bool 
% l.61 \begin{document}
% using Mac TeXlive 20230313_2
% \usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\section{{Roblox} Context}
\label{s:context}
% https://create.roblox.com/docs/scripting/luau

@@

\subsection{Limits of telemetry}

@@

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l}
                 &  Lines &             &    Edit Range & \\
    Mean [std]   &  6,497 & \stddev{22} &         3,680 & \stddev{31} \\
    Median       &  3,115 &             &           926 & \\
    \pct{99}     & 50,547 &             &        34,725 & \\
    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
      & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l} \\
                 & Time Span (sec)  &       & Record Count  \\
    Mean [std]   &     3,184 & \stddev{16}  &     286 & [583] \\
    Median       &       845 &              &     138        \\
    \pct{99}     &    35,450 &              &   3,302        \\
    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
    & \includegraphics[width=0.2\columnwidth]{img/timespan-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/event-count-distribution.pdf}

@@

  \item[For modules that use type analysis:]\leavevmode
    \begin{description}
      \item[Which errors arise?]
        Syntax errors are extremely common~(over \pct{50},~\cref{t:type-error-count}), 
        followed by type mismatches~(\pct{20} in \mstrict{}),
        arity errors~(\pct{2}),
        and failure to unpack on optional value~(\pct{2}).
        There are several uncommon errors, such as misusing a table operation,
        and a few that never arise: internal and too-complex errors,
        duplicating or swapping a generic parameter, use of a deprecated API,
        and unsafe dynamic property lookup on a class.

      \item[How do creators respond? Which errors persist through edits?]
        Creators typically fix analysis errors.
        With few exceptions, increases and decreases in the number of errors
        balance out~(\cref{f:error-changes,t:type-error-survival,}).
        Even in \mnocheck{}, most edits that overlap with syntax errors
        remove at least one error~(\pct{67}) rather than increase or maintain
        the total.
        The errors that most-often survive edits are due to
        inference at a binary operation,
        sending \code{self} to a function that does not expect it,
        and failure to unpack an optional value.
        But the first two seldom arise, and the third is something creators
        might reasonably ignore while prototyping.

>>>>

\usepackage{alltt}
% Not sure why <Programming> is recommending non-standard tools
% \usepackage[backend=biber]{biblatex}
\usepackage[export]{adjustbox}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
% Errors with
% ! Undefined control sequence.
% <argument> \l__siunitx_number_implicit_plus_bool 
% l.61 \begin{document}
% using Mac TeXlive 20230313_2
% \usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\section{Context: {Roblox} and {Luau}}
\label{s:context}
% https://create.roblox.com/docs/scripting/luau

@@

\subsection{Limits of Telemetry}

@@

%  \begin{tabular}{l@{}r@{~}l@{}r@{~}l}
%                 &  Lines &             &    Edit Range & \\
%    Mean [std]   &  6,497 & \stddev{22} &         3,680 & \stddev{31} \\
%    Median       &  3,115 &             &           926 & \\
%    \pct{99}     & 50,547 &             &        34,725 & \\
%    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
%      & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
%    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}
%
%  \end{tabular}

  \begin{tabular}[t]{lrrrl}
    ~          & Mean [std] & Median & \pct{99} Pct. & Distribution \\
    Lines      & 6,497 \stddev{22} & 3,115 & 50,547 & \includegraphics[width=0.14\columnwidth,valign=M]{img/lines-distribution.pdf} \\
    Edit Range & 3,680 \stddev{31} & 926   & 34,725 & \includegraphics[width=0.14\columnwidth,valign=M]{img/editrange-distribution.pdf}
    %% TODO x-axis starts at 1, not zero
    %% TODO much bigger font or much smaller plot!!!

@@

%  \begin{tabular}{l@{}r@{~}l@{}r@{~}l} \\
%                 & Time Span (sec)  &       & Record Count  \\
%    Mean [std]   &     3,184 & \stddev{16}  &     286 & [583] \\
%    Median       &       845 &              &     138        \\
%    \pct{99}     &    35,450 &              &   3,302        \\
%    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
%    & \includegraphics[width=0.2\columnwidth]{img/timespan-distribution.pdf}
%    & & \includegraphics[width=0.2\columnwidth]{img/event-count-distribution.pdf}
%
%  \end{tabular}

  \begin{tabular}{lrrrl} \\
    ~               & Mean [std] & Median & \pct{99} Pct. & Distribution \\
    Time Span (sec) & 3,184 \stddev{16} & 845 & 35,450 & \includegraphics[width=0.14\columnwidth,valign=M]{img/timespan-distribution.pdf} \\
    Record Count    & 286 [583]         & 138 & 3,302  & \includegraphics[width=0.14\columnwidth,valign=M]{img/event-count-distribution.pdf}
    %% TODO x-axis starts at 1
    %% TODO huge font, or smaller plot

@@

  \item[For modules that use type analysis:]\leavevmode
    \begin{description}
      \item[- Which errors arise?]
        Syntax errors are extremely common~(over \pct{50},~\cref{t:type-error-count}), 
        followed by type mismatches~(\pct{20} in \mstrict{}),
        arity errors~(\pct{2}),
        and failure to unpack on optional value~(\pct{2}).
        There are several uncommon errors, such as misusing a table operation,
        and a few that never arise: internal and too-complex errors,
        duplicating or swapping a generic parameter, use of a deprecated API,
        and unsafe dynamic property lookup on a class.

      \item[- How do creators respond? Which errors persist through edits?]
        Creators typically fix analysis errors.
        With few exceptions, increases and decreases in the number of errors
        balance out~(\cref{f:error-changes,t:type-error-survival,}).
        Even in \mnocheck{}, most edits that overlap with syntax errors
        remove at least one error~(\pct{67}) rather than increase or maintain
        the total.
        The errors that most-often survive edits are due to
        inference at a binary operation,
        sending \code{self} to a function that does not expect it,
        and failure to unpack an optional value.
        But the first two seldom arise, and the third is something creators
        might reasonably ignore while prototyping.
